Ant cuticle image classification using texture analysis: a comparative study

### 2022-06-17 paper/main.tex
gaussian filter test
add deep texture section

\author{%
    Noah Gardner\affil{1},
    John Paul Hellenbrand\affil{2},
    Anthony Phan\affil{1},
    Evan Zhu\affil{1},
    Zhiling Long\affil{3},
    Min Wang\affil{2},
    Clint Penick\affil{2},
    and Chih-Cheng Hung\affil{1}\corrauth
}%

@@

\address{%
    \addr{\affilnum{1}}{Laboratory of Machine Vision and Security Research, %
        College of Computing and Software Engineering, Kennesaw State %
        University, Marietta GA, USA}%
    \addr{\affilnum{2}}{College of Science and Mathematics, Kennesaw State
        University, Kennesaw, GA, USA}%
    \addr{\affilnum{3}}{Department of Mathematics, Science, and Informatics,
        Mercer University, Atlanta, GA, USA}%
}
\corraddr{chung1@kennesaw.edu}

@@

\colorbox{green}{TODO: Specifically, what approaches used? Why do we use image
    texture for ant images? What are the contributions?}

@@

@@

% \begin{table}[h]
%     \centering
%     \caption{VGG11 confusion matrix on ant head image dataset.}
%     \begin{tabular}{r|ll}
%                          & True Rough & True Smooth \\
%         \hline
%         Predicted Rough  & 101.75     & 53          \\
%         Predicted Smooth & 37.375     & 257.875     \\
%     \end{tabular}
%     \label{tab:vgg11_confusion_matrix}
% \end{table}

% \begin{table}[h]
%     \centering
%     \caption{VGG13 confusion matrix on ant head image dataset.}
%     \begin{tabular}{r|ll}
%                          & True Rough & True Smooth \\
%         \hline
%         Predicted Rough  & 95.25      & 39.375      \\
%         Predicted Smooth & 43.25      & 272.25      \\
%     \end{tabular}
%     \label{tab:vgg13_confusion_matrix}
% \end{table}

% \begin{table}[h]
%     \centering
%     \caption{VGG16 confusion matrix on ant head image dataset.}
%     \begin{tabular}{r|ll}
%                          & True Rough & True Smooth \\
%         \hline
%         Predicted Rough  & 87.5       & 42.625      \\
%         Predicted Smooth & 47.375     & 272.5       \\
%     \end{tabular}
%     \label{tab:vgg16_confusion_matrix}
% \end{table}

% \begin{table}[h]
%     \centering
%     \caption{VGG19 confusion matrix on ant head image dataset.}
%     \begin{tabular}{r|ll}
%                          & True Rough & True Smooth \\
%         \hline
%         Predicted Rough  & 91.25      & 42.125      \\
%         Predicted Smooth & 43.25      & 273.375     \\
%     \end{tabular}
%     \label{tab:vgg19_confusion_matrix}
% \end{table}

@@

% \begin{figure}[h]
%     \centering
%     \includegraphics[width=0.6\textwidth]{thesis_assets/plots/vgg_average.png}
%     \caption{Average accuracy for VGG architectures on ant head image dataset.}
%     \label{fig:vgg_results}
% \end{figure}

@@

% \begin{table}[h]
%     \centering
%     \caption{ResNet18 confusion matrix on ant head image dataset.}
%     \begin{tabular}{r|ll}
%                          & True Rough & True Smooth \\
%         \hline
%         Predicted Rough  & 98.75      & 48.75       \\
%         Predicted Smooth & 39.25      & 262         \\
%     \end{tabular}
%     \label{tab:resnet18_confusion_matrix}
% \end{table}

% \begin{table}[h]
%     \centering
%     \caption{ResNet50 confusion matrix on ant head image dataset.}
%     \begin{tabular}{r|ll}
%                          & True Rough & True Smooth \\
%         \hline
%         Predicted Rough  & 81.375     & 43.625      \\
%         Predicted Smooth & 55.875     & 269.125     \\
%     \end{tabular}
%     \label{tab:resnet50_confusion_matrix}
% \end{table}

% \begin{table}[h]
%     \centering
%     \caption{ResNet101 confusion matrix on ant head image dataset.}
%     \begin{tabular}{r|ll}
%                          & True Rough & True Smooth \\
%         \hline
%         Predicted Rough  & 85.75      & 53.875      \\
%         Predicted Smooth & 50.125     & 260.25      \\
%     \end{tabular}
%     \label{tab:resnet101_confusion_matrix}
% \end{table}

@@

% \begin{figure}[h]
%     \centering
%     \includegraphics[width=0.6\textwidth]{thesis_assets/plots/resnet_average.png}
%     \caption{Average accuracy for ResNet architectures on ant head image dataset.}
%     \label{fig:resnet_results}
% \end{figure}

@@

% \begin{table}[h]
%     \centering
%     \caption{Fine-tuned ResNet18 confusion matrix on ant head image dataset.}
%     \begin{tabular}{r|ll}
%                          & True Rough & True Smooth \\
%         \hline
%         Predicted Rough  & 117.375    & 35.125      \\
%         Predicted Smooth & 17.875     & 279.625     \\
%     \end{tabular}
%     \label{tab:fresnet18_confusion_matrix}
% \end{table}

% \begin{table}[h]
%     \centering
%     \caption{Fine-tuned ResNet50 confusion matrix on ant head image dataset.}
%     \begin{tabular}{r|ll}
%                          & True Rough & True Smooth \\
%         \hline
%         Predicted Rough  & 114.5      & 33.25       \\
%         Predicted Smooth & 24.125     & 278.125     \\
%     \end{tabular}
%     \label{tab:fresnet50_confusion_matrix}
% \end{table}

% \begin{table}[h]
%     \centering
%     \caption{Fine-tuned ResNet101 confusion matrix on ant head image dataset.}
%     \begin{tabular}{r|ll}
%                          & True Rough & True Smooth \\
%         \hline
%         Predicted Rough  & 117.25     & 33.25       \\
%         Predicted Smooth & 18.375     & 281.125     \\
%     \end{tabular}
%     \label{tab:fresnet101_confusion_matrix}
% \end{table}

@@

% \begin{figure}[h]
%     \centering
%     \includegraphics[width=0.6\textwidth]{thesis_assets/plots/resnet_finetuned_average.png}
%     \caption{Average accuracy for fine-tuned ResNet architectures on ant head image dataset.}
%     \label{fig:fresnet_results}
% \end{figure}

>>>>

\author{%
    Noah Gardner\affil{1},
    John Paul Hellenbrand\affil{2},
    Anthony Phan\affil{1},
    Evan Zhu\affil{1},
    Zhiling Long\affil{4},
    Min Wang\affil{3},
    Clint Penick\affil{2},
    and Chih-Cheng Hung\affil{1}\corrauth
}%

@@

\address{%
    \addr{\affilnum{1}}{Laboratory of Machine Vision and Security Research, %
        College of Computing and Software Engineering, Kennesaw State %
        University, Marietta GA, USA}%
    \addr{\affilnum{2}}{College of Science and Mathematics, Kennesaw State
        University, Kennesaw, GA, USA}%
    \addr{\affilnum{3}}{Department of Mathematics, Kennesaw State University,
        Kennesaw, GA, USA}%
    \addr{\affilnum{4}}{Department of Mathematics, Science, and Informatics,
        Mercer University, Atlanta, GA, USA}%
}
\corraddr{chung1@kennesaw.edu}

@@

\colorbox{green}{\parbox{\dimexpr\textwidth-2\fboxsep}{TODO:Specifically, what
        approaches used? Why do we use image texture for ant images? What are
        the contributions?}}

@@

\subsection{Deep Learning for Texture Analysis}

In the past decade, deep learning using convolutional neural networks (CNNs)
\cite{krizhevsky_imagenet_2017} has emerged as the state-of-the-art technology
for image analysis. Following this trend, various CNN-based network
architectures have been designed to specifically characterize texture images.
Among these, the Fisher-vector CNN descriptor (FV-CNN) proposed by Cimpoi et al.
\cite{cimpoi_describing_2014} is widely accepted as one of the most important
pioneering works. It applies FV pooling to deep features obtained via a CNN
pre-trained using the ImageNet \cite{krizhevsky_imagenet_2017} to obtain encoded
features for texture classification. Although it is capable of achieving much
improved classification accuracy comparing to traditional hand-crafted texture
features, FV-CNN does not support an end-to-end learning, where feature
extraction, encoding, and classification are separated from each other. To
achieve an end-to-end learning, Zhang et al. \cite{zhang_visual_2018} proposed
the deep texture encoding network (DeepTEN), in which a novel texture encoding
layer is added to a standard CNN architecture. Then, Xue et al.
\cite{xue_deep_2018} constructed the deep encoding pooling network (DEP), which
improves over DeepTEN by integrating local spatial characteristics into the
texture representation. Based on DeepTEN and DEP, Hu et al. \cite{hu_multi_2019}
further developed the multi-level texture encoding and representation (MuLTER)
network, which embeds a learnable encoding module at each convolutional layer so
that encoding is performed for both low-level and high-level features, yielding
a multi-level texture representation.

Other network architectures for end-to-end texture learning are also available.
For example, in the deep multiple-attribute-perceived network (MAP-Net)
\cite{zhai_deep_2019}, multiple perceptual attributes are progressively learned
in a mutually reinforced manner through multiple branches. In the deep
structure-revealed network (DSR-Net)\cite{zhai_deep_2020}, inherent structural
representation for a texture pattern is obtained by employing a primitive
capturing module to learn spatial primitives and a dependency learning module to
capture the dependency among the primitives. In \cite{mao_deep_2021}, a residual
pooling layer consisting of a residual encoding module and an aggregation module
is used to generate discriminative features of low dimensions. In
\cite{peeples_histogram_2021}, a histogram layer is designed to compute local
spatial distribution of CNN features. In \cite{chen_deep_2021}, an innovative
aggregation module is presented to exploit statistical self-similarity across
layers. All these architectures customize the standard CNN structure to
accomplish the characterization of certain spatial, visual, or statistical
nature unique to texture images.

@@

@@

@@

@@

@@

@@
